### 2019-11-18 thesis.tex
untouched Vlasov approach
This is the last version before a big change in the previous version of the thesis

>>>>

Above, in the left-hand side, the differential vector operators $\nabla_{\bf r}$
and $\nabla_{\bf v}$ represent, respectively, gradients in space ($x,y,z$) and
velocity ($v_x, v_y,v_z$) coordinates. The quantity ${\bf F}$ is the acting
force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
$\alpha$, which in a fully ionized plasma can assume two values: electrons
$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
variation of the velocity distribution function due to collisional interactions
between the system's particles.

For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, ${\bf E}$
and ${\bf B}$ are the electric and magnetic fields, respectively, and $c$ is
the speed of light.

\section{The Vlasov approach}
\label{vlasov-appr}
